---
title: "Assessing open science practices in phytolith research - figures"
author: "Emma Karoune"
date: "25/09/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Reproducible figures for 'Assessing open science practices in phytolith research'.


### Figure 1: Chart showing a comparison of the number of journal articles per journal in the current study with Lodwick (2019). 

```

```

### Figure 2: Chart showing the location of primary phytolith data in journals sampled (excludes the four journals that contained no articles with primary phytolith data). 

```{r, code=xfun::read_utf8('Fig2-data-location-all-journals.R'), collapse=TRUE}

  
```

### Figure 3: Chart showing the percentage of articles per data location in macro-botanical remains (data taken from Lodwick 2019) and phytoliths.

```


```


### Figure 4: Chart showing the location of phytolith data per year (2009-2018) in the primary phytolith data publications in this study.

```


```


### Figure 5: Chart of percentages for presence/absence questions in this study.

```{r, include=TRUE}
#create lists of data
metadata_list <- c("Reuseable.rawdata", "Pictures", "Open.access", "ICPN.use", "Full.method")
Yes_list <- c(4.4, 74.2, 12.6, 46.9, 68.9)
No_list <- c(95.6, 25.8, 87.4, 53.1, 31.1)

#install and open ggplot2
library(ggplot2)

#remake vectors in accordance with ggplot2 input formatting
metadata <- c(rep("Reusable.rawdata", 2), rep("Pictures", 2), rep("Open.access", 2), rep("ICPN.use", 2), rep("Full.method", 2))
Yes_no <- rep(c("Yes","No"), 5)
Percentage <- c(c(4.4,95.6), c(74.2, 25.8), c(12.6,87.4), c(46.9,53.1), c(68.9,31.1))

print(metadata)
print(Yes_no)
print(Percentage)

#create data frame combining vectors
metadata_table <- data.frame(metadata, Yes_no, Percentage)

#plot stacked bar chart 
ggplot(metadata_table, aes(fill=Yes_no, x=(metadata), y=Percentage)) +
  geom_bar(position="stack", stat = "identity", color="black") + 
  ggtitle("Chart of percentages for presence/absence questions in this study") + ylab("Percentage") + xlab("Presence/absence question")+
  scale_x_discrete(limits = c("Reusable.rawdata", "Pictures", "Open.access", "ICPN.use", "Full.method"))+
  scale_fill_brewer(palette = "Dark2")


```
