---
title: "Assessing open science practices in phytolith research - figures"
author: "Emma Karoune"
date: "25/09/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Reproducible figures for 'Assessing open science practices in phytolith research'.


### Figure 1: Chart showing a comparison of the number of journal articles per journal in the current study with Lodwick (2019). 

```

```

### Figure 2: Chart showing the location of primary phytolith data in journals sampled (excludes the four journals that contained no articles with primary phytolith data). 

```{r, code=xfun::read_utf8('Fig2-data-location-all-journals.R'), collapse=TRUE}

  
```

### Figure 3: Chart showing the percentage of articles per data location in macro-botanical remains (data taken from Lodwick 2019) and phytoliths.

```


```


### Figure 4: Chart showing the location of phytolith data per year (2009-2018) in the primary phytolith data publications in this study.

```


```


### Figure 5: Chart of percentages for presence/absence questions in this study.

```
{r, code=xfun::read_utf8('fig5-secondgo.R'), collapse=TRUE}

```
