---
title: "Assessing open science practices in phytolith research - figures"
author: "Emma Karoune"
date: "25/09/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Reproducible figures for 'Assessing open science practices in phytolith research'.


### Figure 1: Chart showing a comparison of the number of journal articles per journal in the current study with Lodwick (2019). 

```

```

### Figure 2: Chart showing the location of primary phytolith data in journals sampled (excludes the four journals that contained no articles with primary phytolith data). 

```{r, collapse = TRUE}
library(tidyverse)
library(here)

Open_phytos <- read_csv(here("raw data", "Open_Phyto_2020_cleaned.csv"))

Data_location_all_journal <- Open_phytos %>% 
  rename_with(make.names) %>%
  select("Journal", "Data.location") %>% 
  group_by(Journal) %>% 
  count(Data.location)

data_locations_all_percent <- Data_location_all_journal %>% 
  mutate (Percent = n / sum(n) * 100)
  
library(ggplot2)

data_locations_all_percent %>% 
  ggplot(aes(x = factor(Journal), y = Percent, fill = Data.location)) + #selecting the x and y axis values and also the stacked bar fills fpr the legend 
  geom_col(color = "black") + # making a stacked bar chart that has black outline
  theme_minimal() + #graph theme
  labs(title = "Location of phytolith data in journals sampled",
       x = "Journal",
       y = " Percentage of articles") + #labelling the graph
  theme(axis.text.x = element_text(angle = 30, hjust = 1, vjust = 1, size = 8)) +
  scale_x_discrete(limits = c("Vegetation History and Archaeobotany", "Archaeological and Anthropological Sciences", "Environmental Archaeology", "The Holocene", "Journal of Archaeological Science", "Journal of Archaeological Science reports", "Quaternary International", "Antiquity", "Journal of Field Archaeology",	
"Journal of Anthropological Archaeology", "PLoS One","Proceedings of the National Academy of Sciences"), labels = c("VHA", "AAS", "EA", "TH", "JAS", "JASR", "QI", "ANT", "JFA", "JAA", "PO", "PNAS")) +
  scale_fill_brewer(palette = "Dark2", limits = c("N", "Graph", "Table", ".docx", "pdf", ".xlsx", ".csv", "Repository")) #Dark2 is a colour blind friendly palette 
  
```

### Figure 3: Chart showing the percentage of articles per data location in macro-botanical remains (data taken from Lodwick 2019) and phytoliths.

```


```


### Figure 4: Chart showing the location of phytolith data per year (2009-2018) in the primary phytolith data publications in this study.

```


```


### Figure 5: Pie charts of percentages for metadata contained in the articles in this study (recorded as presence or absence): a) Reusable raw data; b) Pictures; c) Open access; d) ICPN use; e) Full method.

```


```
